### 2012-09-21 hdf5/discs_2012/evaluation.tex
A couple of typos found by running aspell on the tex files

In Figure~\ref{write_contig}, we show the write performance for a transfer size of 1MB for contiguous writes, for varying number of processes. It can be seen that the plugin regularly outperforms MPI-IO. However, as we increase the number of processes, its performance falls below that of ad\_plfs. Figure~\ref{read_contig} shows the performance of contigous reads for an unaligned transfer size. The plugin again outperforms MPI-IO, but the performance of ad\_plfs is the best for 64 processes. 
%Figure~\ref{write_interleaved} shows the performance of unaligned writes for a maximum of 8 processes. We set the transfer size here to be 10 bytes more than 1MB. Also, the writes here are interleaved as opposed to contiguous. We see a similar pattern, where the plugin outperforms MPI-IO, but is not as good as that of ad\_plfs for 8 processes. 
Figure~\ref{write_collective} compares the performance of MPI-IO with that of the plugin for collective, unaligned, interleaved writes for a maximum of 8 processes. It is important to note that the plugin outperforms MPI-IO in collective mode. We have not been able to obtain results for collective ad\_plfs due to resource restrictions.

Overall, our results show that although the plugin generally shows good performance, it does not scale as well as we increase the number of processes. This is due to the fact that since we are directly making calls to the PLFS API, the metadata overhead seems to be high. We have all processes participating in file open and close operations, which for large problem sizes can add siginificant overhead. Hence, for future work, we plan to use ad\_plfs directly in the plugin which can overcome this performance drawback, since ad\_plfs has collective optimizations in open and close. It should however be noted that there are some MPI libraries tailored to suit a specific purpose and which do not provide an implementation for MPI-IO. Such libraries can benefit from using a plugin that does not rely on MPI-IO.

>>>>

In Figure~\ref{write_contig}, we show the write performance for a transfer size of 1MB for contiguous writes, for varying number of processes. It can be seen that the plugin regularly outperforms MPI-IO. However, as we increase the number of processes, its performance falls below that of ad\_plfs. Figure~\ref{read_contig} shows the performance of contiguous reads for an unaligned transfer size. The plugin again outperforms MPI-IO, but the performance of ad\_plfs is the best for 64 processes. 
%Figure~\ref{write_interleaved} shows the performance of unaligned writes for a maximum of 8 processes. We set the transfer size here to be 10 bytes more than 1MB. Also, the writes here are interleaved as opposed to contiguous. We see a similar pattern, where the plugin outperforms MPI-IO, but is not as good as that of ad\_plfs for 8 processes. 
Figure~\ref{write_collective} compares the performance of MPI-IO with that of the plugin for collective, unaligned, interleaved writes for a maximum of 8 processes. It is important to note that the plugin outperforms MPI-IO in collective mode. We have not been able to obtain results for collective ad\_plfs due to resource restrictions.

Overall, our results show that although the plugin generally shows good performance, it does not scale as well as we increase the number of processes. This is due to the fact that since we are directly making calls to the PLFS API, the metadata overhead seems to be high. We have all processes participating in file open and close operations, which for large problem sizes can add significant overhead. Hence, for future work, we plan to use ad\_plfs directly in the plugin which can overcome this performance drawback, since ad\_plfs has collective optimizations in open and close. It should however be noted that there are some MPI libraries tailored to suit a specific purpose and which do not provide an implementation for MPI-IO. Such libraries can benefit from using a plugin that does not rely on MPI-IO.
